MPR case study 2

### 2019-12-30 Code/mrp/mrp-vignette.Rmd
Trying to extract stan code from rstanarm

Here is the code that they use to make their '''simulate_mrp_data''' function
```{r}
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5) 
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

@@

  #Make all numeric:
  for (i in 1:ncol(poststrat)) {
    poststrat[, i] <- as.numeric(poststrat[, i])
  }
  for (i in 1:ncol(true_popn)) {
    true_popn[, i] <- as.numeric(true_popn[, i])
  }
  for (i in 1:ncol(sample)) {
    sample[, i] <- as.numeric(sample[, i])
  }
  list(
    sample = sample,
    poststrat = poststrat,
    true_popn = true_popn
  )
}
```
Wow.

Okay back to the case study. 
```{r}
mrp_sim <- simulate_mrp_data(n=1200)
str(mrp_sim)
sample <- mrp_sim[["sample"]]
rbind(head(sample), tail(sample))
```
Using the function to simulate data.

```{r}
poststrat <- mrp_sim[["poststrat"]]
rbind(head(poststrat), tail(poststrat))
```

```{r}
fit <- stan_glmer(cat_pref ~ factor(male) + factor(male) * factor(age) + (1 | state) + (1 | age) + (1 | eth) + (1 | income), 
                  family = binomial(link = "logit"), 
                  data = sample)

library(rstanarm)
example(fit)
rstan::get_stanmodel(fit$stanfit)
```
```{r}
print(fit)
```
```{r}
posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat) 
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N) 
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```
```{r}
sample_popn_pref <- mean(sample$cat_pref)
round(sample_popn_pref, 3)
```
```{r, eval=FALSE}
compare2 <- compare2 +
  geom_hline(yintercept = model_popn_pref[1], colour = '#2ca25f', size = 1) +
  geom_text(aes(x = 5.2, y = model_popn_pref[1] + .025), label = "MRP", colour = '#2ca25f')
bayesplot_grid(compare, compare2, 
               grid_args = list(nrow = 1, widths = c(8, 1)))

```
```{r}
true_ponp_pref <- sum(true_popn$cat_pref * poststrat$N) / sum(poststrat$N) 
round(ttrue_popn_pref, 3)
```

>>>>

Here is the code that they use to make their funtion. 
```{r}
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5) 
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

@@

  #Make all numeric:
  for (i in 1:ncol(poststrat)) {
    poststrat[, i] <- as.numeric(poststrat[, i])
  }
  for (i in 1:ncol(true_popn)) {
    true_popn[, i] <- as.numeric(true_popn[, i])
  }
  for (i in 1:ncol(sample)) {
    sample[, i] <- as.numeric(sample[, i])
  }
  list(
    sample = sample,
    poststrat = poststrat,
    true_popn = true_popn
  )
}
```

Running the function to get simulated data. 
```{r}
mrp_sim <- simulate_mrp_data(n=100)
str(mrp_sim)

sample <- mrp_sim[["sample"]]
poststrat <- mrp_sim[["poststrat"]]
true_popn <- mrp_sim[["true_popn"]]
```
```{r}
fit <- stan_glmer(
  cat_pref ~ factor(male) + factor(male) * factor(age) + 
    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
  family = binomial(link = "logit"),
  data = sample
)
```

Now I am trying to put the data into a list that we can input into stan. 
```{r}
stan_data <- list( 
  K = 5,

  )

# This is the RStanrm function that they use

# fit <- stan_glmer(
#   cat_pref ~ factor(male) + factor(male) * factor(age) + 
#     (1 | state) + (1 | age) + (1 | eth) + (1 | income),
#   family = binomial(link = "logit"),
#   data = sample
# )
```
